### 2021-02-24 manuscript/supplementary.tex
Updated README.md, manuscript and figures.

\PaperTitle{Supplementary results for: A meta-analysis of computational biology benchmarks reveals publication bias affects on speed and accuracy} % Article title

%\Authors{Paul P. Gardner\textsuperscript{1,2}*, James Paterson\textsuperscript{1,2}, Fatemeh Ashari Ghomi\textsuperscript{1,2}, Sinan Uğur Umu\textsuperscript{1,2}, Stephanie McGimpsey\textsuperscript{1,2}} % Authors
%\affiliation{\textsuperscript{1}\textit{School of Biological Sciences, University of Canterbury, Christchurch, New Zealand.}} % Author affiliation
%\affiliation{\textsuperscript{2}\textit{Biomolecular Interaction Centre and the Bio-Protection Research Centre, University of Canterbury, Christchurch, New Zealand.}}
%\affiliation{*\textbf{Corresponding author}: paul.gardner@canterbury.ac.nz} % Corresponding author

\Authors{Paul P. Gardner\textsuperscript{1,2}*, James M. Paterson\textsuperscript{?}, Fatemeh Ashari-Ghomi\textsuperscript{?}, Sinan U. Umu\textsuperscript{?}, Stephanie McGimpsey\textsuperscript{3,4}, Aleksandra Pawlik\textsuperscript{5},
Alex Gavryushkin\textsuperscript{6}, Michael A Black\textsuperscript{1}
} % Authors

\affiliation{\textsuperscript{1}\textit{Department of Biochemistry, University of Otago, Dunedin, New Zealand.}} % Author affiliation
\affiliation{\textsuperscript{2}\textit{Biomolecular Interaction Centre, University of Canterbury, Christchurch, New Zealand.}}
\affiliation{\textsuperscript{3}\textit{McConomy School of Dance, Derry, Ireland.}}
\affiliation{\textsuperscript{4}\textit{Research for Good, Limavady, Ireland.}}
\affiliation{\textsuperscript{5}\textit{New Zealand eScience Infrastructure, 49 Symonds St, Auckland, New Zealand.}}
\affiliation{\textsuperscript{6}\textit{Department of Computer Science, University of Otago, Dunedin, New Zealand.}} % Author affiliation
\affiliation{*\textbf{Corresponding author}: paul.gardner@otago.ac.nz} % Corresponding author

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{hindex-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.45\textwidth]{cites-SpeedVsAccuracy-heatmap.pdf}
\caption{Heatmaps of normalised speed ranks and normalised accuracy
  ranks, both $x$ and $y$ dimensions are discretised into a $10 \times
  10$ matrix. The shading indicates median H-indices for corresponding
  authors (darker shade indicates a higher H) in the figure on the
  left. The shading indicates median citations (on a log scale), for
  software tools in the figure on the right. }
\label{fig:heatmaps}
\end{figure}

\begin{figure}[H]
\centering
%\includegraphics[width=0.95\textwidth]{relAge-SpeedVsAccuracy-heatmap-edited.pdf}
\includegraphics[width=0.45\textwidth]{relAge-speedAcc.pdf}
\includegraphics[width=0.45\textwidth]{relAge-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Left.} Violin plots for the relative age distribution
  for software tools in each of the 5 2x2 cells indicated in B. The
  five boxes correspond to the four extreme corners of the speed vs
  accuracy spectrum (i.e. slow and inaccurate, slow and accurate, fast
  and inaccurate, fast and accurate) and the central box (medium speed
  and medium accuracy). {\bf Right.} A heatmap indicating the relative age
  of software in a range of relative accuracy and speed rankings. Blue
  colours indicate an abundance of older software tools in an accuracy
  and speed category, while light colours indicate younger software in
  an accuracy and speed category. }
\label{fig:ageplot}
\end{figure}

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\bibliographystyle{unsrt}
\bibliography{paulall}

>>>>

\PaperTitle{Supplementary results for: A meta-analysis of bioinformatics software benchmarks reveals that publication-bias unduly influences software accuracy} % Article title

\Authors{Paul P. Gardner\textsuperscript{1,2}*, James M. Paterson\textsuperscript{3}, Stephanie McGimpsey\textsuperscript{4}, Fatemeh Ashari-Ghomi\textsuperscript{5}, Sinan U. Umu\textsuperscript{6}, Aleksandra Pawlik\textsuperscript{7},
Alex Gavryushkin\textsuperscript{8}, Michael A Black\textsuperscript{1}
} % Authors

\affiliation{\textsuperscript{1}\textit{Department of Biochemistry, University of Otago, Dunedin, New Zealand.}} % Author affiliation
\affiliation{\textsuperscript{2}\textit{Biomolecular Interaction Centre, University of Canterbury, Christchurch, New Zealand.}}
\affiliation{\textsuperscript{3}\textit{Department of Civil and Natural Resources Engineering, University of Canterbury, Christchurch, New Zealand.}}
\affiliation{\textsuperscript{4}\textit{Parasites and Microbes, Wellcome Sanger Institute, Wellcome Genome Campus, Hinxton,
8 Cambridgeshire, CB10 1RQ, UK.}}
\affiliation{\textsuperscript{5}\textit{Research Group for Genomic Epidemiology, National Food Institute, Technical University of Denmark, Kongens Lyngby, Denmark.}}
\affiliation{\textsuperscript{6}\textit{Department of Research, Cancer Registry of Norway, Oslo, Norway.}} % Author affiliation
\affiliation{\textsuperscript{7}\textit{New Zealand eScience Infrastructure, 49 Symonds St, Auckland, New Zealand.}}
\affiliation{\textsuperscript{8}\textit{Department of Computer Science, University of Otago, Dunedin, New Zealand.}} % Author affiliation

\affiliation{*\textbf{Corresponding author}: paul.gardner@otago.ac.nz} % Corresponding author

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{hindex-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.45\textwidth]{cites-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Citation metrics and software tool speeds/accuracies.} Heatmaps of normalised speed ranks and normalised accuracy
  ranks, both $x$ and $y$ dimensions are discretised into a $10 \times
  10$ matrix. The shading indicates different median citation-based
  feature scores (redder shade indicates a higher value).  The shading
  indicate median H-indices ({\bf left}) and $log_{10}(citations)$
  ({\bf right}). }
\label{fig:heatmaps}
\end{figure}

\begin{figure}[H]
\centering
%\includegraphics[width=0.95\textwidth]{relAge-SpeedVsAccuracy-heatmap-edited.pdf}
\includegraphics[width=0.45\textwidth]{relAge-speedAcc.pdf}
\includegraphics[width=0.45\textwidth]{relAge-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Relative software tool ages and speeds/accuracies.} {\bf Left.} Violin plots for the relative age distribution
  for software tools in each of the 5 2x2 cells indicated in B. The
  five boxes correspond to the four extreme corners of the speed vs
  accuracy spectrum (i.e. slow and inaccurate, slow and accurate, fast
  and inaccurate, fast and accurate) and the central box (medium speed
  and medium accuracy). {\bf Right.} A heatmap indicating the relative age
  of software in a range of relative accuracy and speed rankings. Blue
  colours indicate an abundance of older software tools in an accuracy
  and speed category, while light colours indicate younger software in
  an accuracy and speed category. }
\label{fig:ageplot}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{commits-SpeedVsAccuracy-heatmap.pdf}
\includegraphics[width=0.45\textwidth]{contributors-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Version control use and software tool speeds/accuracies.}
  Heatmaps of normalised speed ranks and normalised accuracy
  ranks, both $x$ and $y$ dimensions are discretised into a $10 \times
  10$ matrix. The shading indicates different median github-derived
  feature scores (redder shade indicates a higher value).  The shading
  indicate the number of commits ({\bf left}) and the number of code contributors
  ({\bf right}).
 }
\label{fig:heatmapsCommits}
\end{figure}

The complete list of benchmarks used for this study
\cite{pmid32183840,
pmid32138645,
pmid31948481,
pmid31874603,
pmid31984131,
pmid31639029,
pmid31465436,
pmid31324872,
pmid31159850,
pmid31136576,
pmid31080946,
pmid31015787,
pmid30936559,
pmid30717772,
pmid30658573,
pmid29568413,
pmid28934964,
pmid28808243,
pmid28739658,
pmid28569140,
pmid28052134,
pmid27256311,
pmid26862001,
pmid26778510,
pmid26628557,
pmid26220471,
pmid25777524,
pmid25760244,
pmid25574120,
pmid25521762,
pmid25511303,
pmid25198770,
pmid24839440,
pmid24708189,
pmid24602402,
pmid24526711,
pmid24086547,
pmid23842808,
pmid23758764,
pmid23593445,
pmid23393030,
pmid22574964,
pmid22506536,
pmid22492192,
pmid22287634,
pmid22152123,
pmid22172045,
pmid22132132,
pmid21856737,
pmid21615913,
pmid21525877,
pmid21483869,
pmid21423806,
pmid21113338,
pmid20617200,
pmid20047664,
pmid19179695,
pmid19126200,
pmid19046431,
pmid18793413,
pmid18287116,
pmid17151342,
pmid17062146,
pmid15840834,
pmid15701525,
ng2013estimating}.

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\bibliographystyle{unsrt}
\bibliography{supp-references}
